[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

>>>>

Looking to "Religion, England and Wales: Census 2021" from the *Office for National Statistics* provides further insight on whether or not religious identification and marriage ceremony type are congruent in their data. In the 2021 census, 46.2% (27.5 million) identified as Christian in comparison to 59.3% (33.3 million) in 2011 [@census2021]. Although Christianity still remains the most popular religion in England and Wales, the decrease over a decade is still somewhat significant as less than half the population now identifies as Christian. This reflected on a smaller level in the marriage ceremony data, as seen in @fig-oppositereligiousten, since all Christian sects experienced a decline in annual marriage ceremonies with the Church of England seeing a reduction of just under 40,000 ceremonies in 2020 compared to 2011.
